\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-21 forwards-and-backwards.tex
moar lookdown bits

%% %% %% %% %% %% %% %% %% %% %% %%
\subsection{Evolution of an Individual Particle}
\label{sec: Evolution of an Individual Particle}

>>>>

%% %% %% %% %% %% %% %% %% %% %% %%
\subsection{Construction of individual lineages}

Although we will \comment{later} show convergece of the lookdown process
defined by Definition~\ref{defn:lookdown_mgale}
to a stochastic process in which individuals retain their identities,
it is convenient to construct the lookdown process
in a way that explicitly represents the motion of each individual and their offspring.
This will then make obvious how linages move in the limit.

We will construct the process using a Ulam-Harris indexing scheme,
which associates the outcomes of each branching event with a label obtained
by appending to the previous label.
To begin, we assign each extant individual a label from $\IN_{\ge 0}$.
Suppose an individual with label $a$ and level $u$ reproduces,
and as a result there are two individuals, one with level $u$ and one with a new level $u_1 > u$.
The parent individual, previously labeled $a$, might be assigned either level.
After reproduction, we give a new label to \emph{only} the individual
that is given the new level $u_1$,
retaining the label $a$ for the individual with the old level $u$.
So, there is a unique label assigned at each birth event,
and it is assigned to the resulting individual with the higher level.
It would be possible to reconstruct individual identities along a line of descent
from this construction,
but we don't write this out.

Concretely, then: for each label $a$ in
$\labelspace = \bigcup_{k \ge 1} \IN_{\ge 1}^k$
let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
The mean measure is a product of Lesbegue measure on the first three coordinates
and $q(0, \cdot)$ on the remainder.
For a point $(t, v, y, kappa)$ in $\Pi_a$,
first $t$ will determine possible birth times,
$v$ will determine levels of the offspring,
$y$ will give the spatial displacement of the offspring relative to the parent,
and $\kappa$ will be used to determine whether parent or offspring are assigned the new level.
Each label $a$ has a birth time $\tau_a$,
when it is first assigned,
and a death time $\sigma_a$, when its level first hits $\lambda$.
For any $\tau_a \le t \le \sigma_a$ we denote by $X_a(t)$ and $U_a(t)$ the spatial location and level
of the individual carrying label $a$ at time $t$.
Now, since we have defined labels so that the level does not jump,
$U_a$ satistifies, for $\tau_a \le t \le \sigma_a$,
\begin{equation*}
    \begin{split}
& U_a(t)
    =
    U_a(\tau_a) \\
&\qquad {}   
    + \int_{\tau_a}^{t}
    \left(
        \frac{\theta}{\lambda} \gamma(X_a(s),\eta(s)) \int_{\IR^d} r(y,\eta(s)) q(X_a(s),dy) U_a(s)^2
        -
        b(X_a(s),\eta(s)) U_a(s)
    \right)
    ds ,
\end{split}
\end{equation*}
and, of course, $\sigma_a = \inf\{t \ge \tau_a : U_a(t) > \lambda\}$.

Potential reproduction events occur at times $\tau_a + s$ for each point $(s, v, y, \kappa) \in \Pi_a$.
We say `potential' since if the resulting level is greater than $\lambda$,
the event does not happen.
If this is the $j^\text{th}$ such successful event,
\comment{(need to sort out the "successful" qualifier)}
the new level is $aj$ (i.e., $a$ with the integer $j$ appended),
and the (potential) new level is
\begin{equation*}
    U_{aj}(\tau_a + s)
    =
    U_a(\tau_a + s)
    +
    \frac{
        v
    }{
        2 \lambda^{-1} \theta \gamma(X_a(\tau_a + s-), \eta(\tau_a + s-))
        \int_{\IR^d} r(y, \eta(\tau_a + s-)) q(X_a(\tau_a + s-), dy)
    }.
\end{equation*}
If $U_{aj}(\tau_a+s) < \lambda$,
a new individual is produced with this level, label $aj$ and
location 
$$
    X_{aj}(\tau_a + s)
    =
    X_a(\tau_a+s-) + (1 - \kappa) y .
$$
If $\kappa=1$, then it is the original label that moves spatial locations, so
$$
    X_a(\tau_a+s)
    =
    X_a(\tau_a+s-) + \kappa y .
$$

%% %% %% %% %% %% %% %% %% %% %% %%
\subsection{PREVIOUS VERSION OF Evolution of an Individual Particle}
\label{sec: Evolution of an Individual Particle}
